On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-03-29 manuscripts/PNAS/chazthm_pnas.tex
lem

%%% CHAZ TODO %%%
% replace dictionary learning with 'sparse linear coding'

@@

\begin{lemma}\label{NonEmptyLemma} 
Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property. If there exists a map $\pi: E \to 2^{[m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S | \ \ \text{for all } F \subseteq E,
\end{align}
%
then $\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
\end{lemma}
\begin{proof}
Fix $T = \{(j, S): j \in \pi(S), S \in E\}$. We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$. Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular. Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.

>>>>

%%% CHAZ TODO %%%

@@

\begin{lemma}\label{NonEmptyLemma} 
Fix integers $\ell$ and $m \leq \hat m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property. If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S | \ \ \text{for all } F \subseteq E,
\end{align}
%
then the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$. In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
%$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
\end{lemma}
\begin{proof}
[* TODO * Chris rewrite for $\hat m$] Fix $T = \{(j, S): j \in \pi(S), S \in E\}$. We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$. Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular. Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.
